Fourmile

### 2022-10-11 fourmile_dataprocess.Rmd
brought precip figs back in

```{r precip, echo=F}
#daily precip
# prec_update <- prec %>%
#   mutate(date = dmy(date),
#          doy = yday(date)) %>%
#   mutate_at(c('Gordon_South', 'Gordon_North',
#               'GH', 'LM', 'SE', 'SP', 'ST', 'NADP_SL'),
#             ~(ifelse(!doy %in% c(152:258), 
#                                NA, .))) %>%
#   mutate_at(c('prism_W', 'prism_M', 'prism_E'), list(lead), n = 1) %>%
#   mutate_at(c('prism_W', 'prism_M', 'prism_E'), ~(ifelse(doy %in% c(152:258),
#                                                          NA, .))) %>%
#   filter(date > '2009-12-31') %>%
#   dplyr::select(-c(doy)) %>%
#   mutate(date = format(as.Date(date), '%d.%m.%Y'))
# 
# #write_csv(prec_update, 'precipAll_update.csv')
# 
# daily_p <- prec %>%
#   mutate(date = dmy(date)) %>%
#   replace(.==-9999, NA) %>%
#   pivot_longer(!date, names_to = 'site', values_to = 'precip_mm') %>%
#   mutate(precip_mm = as.numeric(precip_mm)) %>%
#   mutate(WY = calcWaterYear(date)) %>%
#   group_by(WY, site) %>%
#   mutate(dailyp_cum_mm = cumsum(precip_mm))
# 
# precip <- ggplot(daily_p, aes(x=date, y=precip_mm, color=site)) + geom_line()  +
#   theme_bw() +
#   ggtitle('Daily precip (all)')
# 
# ggplotly(precip)
# 
# precip_cumu <- ggplot(daily_p, aes(x=date, y=dailyp_cum_mm, color=site)) + geom_line()  +
#   theme_bw() +
#   ggtitle('Daily precip cumulative sums (all)')
# 
# ggplotly(precip_cumu)

>>>>

```{r precip, echo=F}
#daily precip
prec_update <- prec %>%
  mutate(date = dmy(date),
         doy = yday(date)) %>%
  mutate_at(c('Gordon_South', 'Gordon_North',
              'GH', 'LM', 'SE', 'SP', 'ST', 'NADP_SL'),
            ~(ifelse(!doy %in% c(152:258),
                               NA, .))) %>%
  mutate_at(c('prism_W', 'prism_M', 'prism_E'), list(lead), n = 1) %>%
  mutate_at(c('prism_W', 'prism_M', 'prism_E'), ~(ifelse(doy %in% c(152:258),
                                                         NA, .))) %>%
  filter(date > '2009-12-31') %>%
  dplyr::select(-c(doy)) %>%
  mutate(date = format(as.Date(date), '%d.%m.%Y'))

#write_csv(prec_update, 'precipAll_update.csv')

daily_p <- prec %>%
  mutate(date = dmy(date)) %>%
  replace(.==-9999, NA) %>%
  pivot_longer(!date, names_to = 'site', values_to = 'precip_mm') %>%
  mutate(precip_mm = as.numeric(precip_mm)) %>%
  mutate(WY = calcWaterYear(date)) %>%
  group_by(WY, site) %>%
  mutate(dailyp_cum_mm = cumsum(precip_mm))

precip <- ggplot(daily_p, aes(x=date, y=precip_mm, color=site)) + geom_line()  +
  theme_bw() +
  ggtitle('Daily precip (all)')

ggplotly(precip)

precip_cumu <- ggplot(daily_p, aes(x=date, y=dailyp_cum_mm, color=site)) + geom_line()  +
  theme_bw() +
  ggtitle('Daily precip cumulative sums (all)')

ggplotly(precip_cumu)
